Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-13 paper.tex
finished pegasus summary

        \subsection{Debugging and provenance}
         Job monitoring, in Pegasus, is achieved through \textit{pegasus-kickstart} (kickstart). Every job within a pegasus workflow has a kickstart wrapper that collects runtime provenance
        and performance. Kickstart relays this information to the submit host after job completion.

>>>>

        \subsection{Debugging and provenance}
         Job monitoring, in Pegasus, is achieved through \textit{pegasus-kickstart} (kickstart). Every job within a pegasus workflow has a kickstart wrapper that collects runtime provenance
        and performance. Kickstart relays this information to the submit host after job completion. This data is ultimately collected and stored in a relational database.

        The Mapper Logs contain details on the abstract workflow, the jobs in the executable workflow 
        and the mapping of tasks to jobs. Using the mapper logs, Pegasus can generate the provenance of the results. Should it be required, Pegasus can also generate the provenance of the 
        mapping process.

        In addition to the Mapper Logs, there also exists the DAGMan logs, generated by HTCondor DAGMan and updated in near real-time. These logs capture details on the status of the jobs
        and their associated pre- and post- execute scripts.

        All provenance and debugging data is accessibly through either the \textit{pegasus-analyzer} tool or through the provided lightweight web interface.
